%-------------------------
% Resume in Latex
% Author : Abhishek Ghimire
% Based off of: https://github.com/cypherab01/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%% RESUME STARTS HERE %%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://abhishekg.com.np/}{\Large Abhishek Ghimire}} & Email : \href{mailto:aghimire074@gmail.com}{aghimire074@gmail.com}\\
  \href{https://github.com/cypherab01}{github.com/cypherab01} & Mobile : 984-7526298 \\
  \href{http://linkedin.com/in/cypherab01}{linkedin.com/in/cypherab01} & {Balkhu, Kathmandu}\\
\end{tabular*}

%-----------SUMMARY-----------
\section{Summary}
Passionate 8th-semester IT student with hands-on experience in modern web development through academic projects and professional internships. Skilled in building responsive applications using Next.js, React, Tailwind CSS, and shadcn/ui, with demonstrated ability to create full-stack solutions. Seeking to leverage strong technical foundation in JavaScript frameworks and collaborative problem-solving skills to contribute as a Next.js Developer Junior Developer. Eager to grow within a dynamic team while delivering efficient, user-centric web solutions.

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Next.js Developer Intern}{Jan 2025 -- Present}
      {Treeleaf Technologies}{Lalitpur, Nepal}
    \resumeItemListStart
        \resumeItem{Developed and maintained front-end components for web applications using Next.js, React, and related technologies.}
        \resumeItem{Collaborated with senior developers to implement new features and improve existing codebase.}
        \resumeItem{Gained hands-on experience with modern web development workflows and best practices.}
    \resumeItemListEnd
    
    \resumeSubheading
      {CloudWorker (Part-time)}{December 2023 -- Present}
      {CloudFactory, Nepal}{Remote}
    \resumeItemListStart
        \resumeItem{Annotated diverse datasets, including images, text, and audio, to support AI and machine learning projects.}
        \resumeItem{Ensured high-quality and accurate data labeling by adhering to detailed project guidelines.}
        \resumeItem{Managed tasks and met deadlines efficiently in a remote, flexible work environment.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Notebook} $|$ \emph{Next.js, JWT, MongoDB, shadcn/ui}}{\href{https://notebook.abhishekg.com.np}{notebook.abhishekg.com.np}}
          \resumeItemListStart
            \resumeItem{Developed a full-stack note-taking application with protected REST APIs and JWT authentication.}
            \resumeItem{Implemented secure routes using Next.js middleware and modern UI with shadcn/ui components.}
            \resumeItem{Integrated MongoDB for data persistence and Nodemailer for account verification emails.}
          \resumeItemListEnd
          
     \resumeProjectHeading
    {\textbf{bitinfoNepal} $|$ \emph{Next.js, Web Scraping}}{\href{https://bitinfonepal.com}{bitinfonepal.com}}
    \resumeItemListStart
      \resumeItem{Created an educational platform for BIT students featuring automated notice scraping and email notifications.}
      \resumeItem{Built a comprehensive resource hub with syllabus materials, notes, and past examination questions.}
      \resumeItem{Implemented content filtering system to display relevant BIT-specific notices to students.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
\resumeSubHeadingListStart
  \resumeSubSubheading{Technical Skills}{}
  \resumeItemListStart
    \resumeItem{\textbf{Front-End Development:} HTML5, CSS3, JavaScript, React, Next.js, Tailwind CSS, shadcn/ui}
    \resumeItem{\textbf{Back-End Development:} Next.js APIs, MongoDB}
    \resumeItem{\textbf{Tools:} Git, GitHub, Visual Studio Code, Cursor}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
  \resumeSubSubheading{Interpersonal Skills}{}
  \resumeItemListStart
    \resumeItem{\textbf{Communication:} Effectively communicate technical concepts to both technical and non-technical audiences.}
    \resumeItem{\textbf{Collaboration:} Proven ability to work effectively in team settings on various projects.}
    \resumeItem{\textbf{Problem-Solving:} Analytical thinking and creative solutions to technical challenges.}
    \resumeItem{\textbf{Attention to Detail:} Focused on code quality, UI consistency, and thorough testing to ensure error-free products.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Patan Multiple Campus}{Patandhoka, Lalitpur}
      {Bachelors in Information and Technology, IOST, TU}{Mar. 2021 -- May 2025 (Expected)}
    \resumeSubheading
      {Deep Boarding High School}{Butwal, Lumbini}
      {Physical Science with Computer Science}{July 2018 -- Oct. 2020}
  \resumeSubHeadingListEnd



%-------- Awards and Achievements ---------
\section{Awards \& Achievements}
\resumeSubHeadingListStart
    \resumeSubheading
      {NDG Linux Unhatched English 0424a}{April 2024}
      {Mastered Linux command line basics through NDG Linux Unhatched course}{}
    \resumeItemListStart
        \resumeItem{Acquired foundational skills in Linux operation and management.}
    \resumeItemListEnd
    
    \resumeSubheading
      {Deep Web - The Complete Understanding of the Hidden Web}{March 2024}
      {Understood the concept of Dark Web \& Deep Web}{}
    \resumeItemListStart
        \resumeItem{Explored Deep Web concepts and security implications.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}